Validating FF-Replan vs.\@ a State-Of-The-Art Probabilistic Planner in Translated Real World Domains

### 2014-03-29 FinalPaper/paper.tex
Small addition to the problem definition of replanners
gourmand added

\subsection{Planning problem}
\begin{itemize}
	\item Describe the MDP finite horizon planning problem
	\item reason about the \emph{augmented state space} of M(H), which is a set \emph{S x (0, ... , H)} of state number of steps-to-go pairs
	\item Describe reward heuristic
	\item Solving M(H) means finding a policy: a rule for selecting actions in augmented states so that executing the actions recommended by the policy starting in the initial state will accumulate the largest exected reward over H steps time
	\item The challenge or large branching factors (induced by natural dynamic)
\end{itemize}

@@

\subsection{LRTDP vs. UCT for Online Probabilistic Planning\cite{kolobov2012gourmand}}

>>>>

\subsection{Planning problem}
\begin{itemize}
	\item Describe the MDP finite horizon planning problem (usefull for modelling nearly inifinite processes)
	\item reason about the \emph{augmented state space} of M(H), which is a set \emph{S x (0, ... , H)} of state number of steps-to-go pairs
	\item Describe reward heuristic
	\item Solving M(H) means finding a policy: a rule for selecting actions in augmented states so that executing the actions recommended by the policy starting in the initial state will accumulate the largest exected reward over H steps time
	\item The challenge or large branching factors (induced by natural dynamic)
\end{itemize}

@@

\subsection{LRTDP vs. UCT for Online Probabilistic Planning\cite{kolobov2012gourmand}}
During IPPC-2011 1 out of 5 planners used a LRTDP-based system and managed to outperform three other planners using the dominant algorithm for probabilistic planning: UCT. This caused to wonder whether LRTDP planners could outperform UCT based systems.  UCT forces an expert to guess a non-shortsighted lookahead value for which it should be able to converge on encountered states. Choosing this value can have very bad consequences and its existence causes the UCT to require some input, taking away from its autonomicity. At the IPPC-2011 GLUTTON was an offline LRTDP based planner that came second. As PROST employed UCT in an online manner, GOURMAND is an online adaptation of the GLUTTON algorithm to test whether LRTDP performs better if it is employed online.

UCT picks an action based on it current quality estimate and an \emph{exploration term} which forces the planner to choose actions that have rarely been tried in the past. This makes UCT suitable for a wider scale of scenarios but also implies an unreliable termination condition.

Because real world domains contain Natural Dynamics that introduce large branching factors, offline planning is often a waste of time and memory space since there is a vast amount of state the planner may never reach in a lifetime. Such problems are far better solved using online planners by finding a $\tau$* or an approximation for the current state, executing it and repeating. This is done by choosing a certain lookahead  L and solving MDP \emph{M\textsubscript{s}(L)} to solve \emph{M\textsubscript{0}(H)} where L $<$ H and then select \emph{$\pi$*\textsubscript{L}(s, L)} recommended by the optimal policy. This lookahead value is determined using the per-process time constraint.

\subsubsection{GOURMAND}
In contrast to GLUTTON, GOURMAND always makes an informed choice in any state where it ends up when the time T allocated for solving the MDP runs out because of the online fashion it uses LRTDP. GOURMAND first divides the time among all remaining epochs, determines the largest lookahead L for which it can almost certainly solve any remaining epoch if T is assigned.  It then checks if it can solve even for a larger lookahead L by taking away a small configuration time from future epochs  while still guaranteeing that it can solve for Lookahead L in each of them. This was GOURMAND adaptively picks a good lookahead value at each desicion epoch given the per-process constraint T. This can only be achieved by knowing how long it takes for LRTDP to solve a state for certain lookahead values. It uses LR\textsuperscript{2}TDP to collect this data. This version of LRTDP is more efficient because of the early convergences and it allows measuring how long on average the solving of a task takes. GOURMAND uses the same engineering optimizations to to handle evaluate actions, iterating over the successors of s under a by the Bellman Backups. GOURMAND eventually outperforms both GLUTTON and PROST, the winner of the IPPC-11\cite{keller2012prost}.
